Sampling-Based Motion Planning for Tracking Evolution of Dynamic Tunnels in Molecular Dynamics Simulations

### 2017-10-31 paper.tex
qinit^i replaced

One tunnel is defined by the exit point and by the active site.
If both these nodes are connected to the same component of the graph, they define a static tunnel.
Such a tunnel can be reconstructed by finding a path between these two nodes in the graph.
If there does not exist any path between the exit point $p \in P^i$ (the exit point at frame $i$) and the active site $\qinit \in \CF^i$ in the same frame, the dynamic tunnel has to start from a different active site (in one of the previous frames).
A path from $p \in P^i$ to the first active site $\qinit\in\CF^i$ reachable in the graph (measured by the number of edges) describes the dynamic tunnel.
An example is depicted in Fig.~\ref{fig::components}.

>>>>

One tunnel is defined by the exit point and by the active site.
If both these nodes are connected to the same component of the graph, they define a static tunnel.
Such a tunnel can be reconstructed by finding a path between these two nodes in the graph.
If there does not exist any path between the exit point $p \in P^i$ (the exit point at frame $i$) and the active site $\qinit \in \CF^i$ in the same frame, the dynamic tunnel has to start from a different active site (in one of the previous frames).
A path from $p \in P^i$ to the first active site $\qinit\in\CF^j, j < i$ reachable in the graph (measured by the number of edges) describes the dynamic tunnel.
An example is depicted in Fig.~\ref{fig::components}.
